A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-12-30 pilot-publication/lab-book.Rmd
Use bca instead of basic bootstrap CIs

@@

## Combine point estimates and confidence intervals into a single table
combined.outcome.results <- lapply(ci.levels, function(ci.level) {
    lapply(cell.references, function(cell.reference) {
        point.estimate <- outcome.results$point.estimates[[cell.reference]]
        ci.data <- outcome.results$confidence.intervals[[cell.reference]]
        ci <- ci.data[ci.data[, 1] == ci.level, c("lower", "upper")]
        combined <- NA
        if (!all(is.na(ci))) {
            ## combined <- sprintf("%0.2f", c(point.estimate, ci))
            combined <- paste0(combined[1], " (", combined[2], ", ", combined[3], ")")
        }
        return(combined)
    }) %>%
        setNames(cell.references)
}) %>%
    setNames(paste0("ci.level.", ci.levels))

@@

```{r}
## Error in `add_column()`:
## ! New columns must be compatible with `.data`.
## ✖ New column has 112 rows.
## ℹ `.data` has 111 rows.
## Backtrace:
##     ▆
##  1. ├─boot::boot(data, estimate_outcome_results, R = n.boot.samples)
##  2. │ └─global statistic(data, original, ...)
##  3. │   └─outcomes.tables$absolute.difference %>% as_tibble() %>% ...
##  4. └─tibble::add_column(., outcomes.row.names, .before = 1)
##  5.   └─tibble:::abort_incompatible_new_cols(nrow(.data), df)
##  6.     └─tibble:::tibble_abort(...)
##  7.       └─rlang::abort(x, class, ..., call = call, parent = parent, use_cli_format = TRUE)
## Execution halted
```

@@

```{r}
## Error in Ops.data.frame(outcomes.tables$post.training[2:4], outcomes.tables$pre.training[2:4]) :
##   ‘-’ only defined for equally-sized data frames
## Calls: boot -> statistic -> Ops.data.frame
## Execution halted
```

>>>>

## Import bootstrapped outcome results and generate confidence intervals

```{r}
## Load bootstrapped outcome results
bootstrapped.outcome.results <- readRDS(file.path("out", "bootstrapped-outcome-results.Rds"))
str(bootstrapped.outcome.results, max.level = 1)

## Calculate confidence intervals
bootstrapped.outcome.results.ci <- calculate_bootstrap_cis(bootstrapped.outcome.results)

## Combine point estimates with confidence intervals
outcome.results <- list(
    point.estimates = bootstrapped.outcome.results$t0,
    confidence.intervals = bootstrapped.outcome.results.ci
)
saveRDS(outcome.results, file = file.path("outcome-results.Rds"))
```

@@

## Combine point estimates and confidence intervals into a single table
combined.outcome.results <- lapply(ci.levels, function(ci.level) {
    lapply(cell.references, function(cell.reference) {
        point.estimate <- outcome.results$point.estimates[[cell.reference]]
        ci.data <- outcome.results$confidence.intervals[[cell.reference]]
        ci <- ci.data[ci.data[, "level"] == ci.level, c("lower", "upper")]
        combined <- NA
        if (!all(is.na(ci))) {
            combined <- round(c(point.estimate, ci), 2)
            combined <- paste0(combined[1], " (", combined[2], ", ", combined[3], ")")
        }
        return(combined)
    }) %>%
        setNames(cell.references)
}) %>%
    setNames(paste0("ci.level.", ci.levels))

@@

```{r}
## Error in `add_column()`:
## ! New columns must be compatible with `.data`.
## <U+2716> New column has 112 rows.
## <U+2139> `.data` has 111 rows.
## Backtrace:
##     <U+2586>
##  1. <U+251C><U+2500>boot::boot(data, estimate_outcome_results, R = n.boot.samples)
##  2. <U+2502> <U+2514><U+2500>global statistic(data, original, ...)
##  3. <U+2502>   <U+2514><U+2500>outcomes.tables$absolute.difference %>% as_tibble() %>% ...
##  4. <U+2514><U+2500>tibble::add_column(., outcomes.row.names, .before = 1)
##  5.   <U+2514><U+2500>tibble:::abort_incompatible_new_cols(nrow(.data), df)
##  6.     <U+2514><U+2500>tibble:::tibble_abort(...)
##  7.       <U+2514><U+2500>rlang::abort(x, class, ..., call = call, parent = parent, use_cli_format = TRUE)
## Execution halted
```

@@

```{r}
## Error in Ops.data.frame(outcomes.tables$post.training[2:4], outcomes.tables$pre.training[2:4]) :
##   <U+2018>-<U+2019> only defined for equally-sized data frames
## Calls: boot -> statistic -> Ops.data.frame
## Execution halted
```
